An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps

### 2019-02-21 algorithm_radix.Rmd
Need to include data in centroids for plotting end_cents

# Select only desired LGA areas, those from tas.
tas_sa2[[sf_id]] <- droplevels(as.factor(tas_sa2[[sf_id]]))

@@

```{r, fig.cap="tas Local Government Areas and derived centroids."}
end_cents <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude, colour = log(AREASQKM16)), data= centroids) + theme_void() + coord_equal()
end_cents

@@

```{r}
hex_points_df <- centroid_allocation %>% 
  group_by(SA2_5DIG16) %>%
  nest() %>%
  mutate(hex_points = 
      map(.x = data,.f = function(a) { 
        fortify_hexagon(data = a, hex_size = hex_size)})) %>%
  unnest(data) %>%
  unnest(hex_points)
```

@@

```{r fullhexmap}
lga_map <- create_hexmap(shp = tas_sa2, sf_id = "SA2_5DIG16", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)

hexmap_lga <- left_join(tas_sa2, 
  lga_map)

```{r}
end_hex <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") +
  theme_void() + coord_equal() +
    geom_hex(aes(x = hex_long, y = hex_lat, fill = AREA_SQKM), data = hexmap_lga, 
      position = "identity", stat = "identity")

>>>>

# Select only desired SA2 areas, those from tas.
tas_sa2[[sf_id]] <- droplevels(as.factor(tas_sa2[[sf_id]]))

@@

```{r, fig.cap="tas Local Government Areas and derived centroids."}
end_cents <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids) + theme_void() + coord_equal()
end_cents

@@

```{r}
hex_points_df <- centroid_allocation %>% 
  group_nest(SA2_5DIG16) %>%
  mutate(hex_points = 
      map(.x = data,.f = function(a) { 
        fortify_hexagon(data = a, hex_size = hex_size)})) %>%
  unnest(data) %>%
  unnest(hex_points)
```

@@

```{r fullhexmap}
# Create centroids set
centroids <- create_centroids(tas_sa2, "SA2_5DIG16")
# Create hexagon location grid
grid <- create_grid(centroids = centroids, hex_size = 0.1, buffer_dist = 0.1)
# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(centroids = centroids,
hex_grid = grid,
hex_size = 0.1, # same size used in create_grid
filter_dist = 0.25,
focal_points = sugaRbag::capital_cities,
width = 30,
id = "SA2_5DIG16", verbose = TRUE) # same column used in create_centroids
```

```{r}
h1 <- hex_allocated %>%
  dplyr::group_nest(SA2_5DIG16) %>%
                mutate(hex = purrr::map(data, fortify_hexagon, hex_size = 0.1)) %>%
                unnest(data) %>% 
  unnest(hex) %>% left_join(., tas_sa2)

p1 <- fortify_sfc(tas_sa2)

ggplot(mapping = aes(fill = SA4_NAME16)) +
  geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
  geom_polygon(data = h1, aes(x=hexv_long, hexv_lat, group = SA2_5DIG16))
